---
title: "Study on Residents' Needs Base on Apartment Building Evaluation"
author: "Guangyu Du"
date: 2015-07-23T21:13:14-05:00
bibliography: "reference.bib"
categories: ["R"]
tags: ["R Markdown", "plot", "regression"]
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(collapse = TRUE)
```

## Author: Guangyu Du

# Abstact
There exist a substantial amount of residents living in Toronto's apartment buildings. In this paper we explore the Apartment Building Evaluation dataset, which was a survey conducted by OPENDATA Toronto. In this project, we focus on three important basics of the apartments' condition which are: the security, lobby condition and parking area condition. And the result shows that majority of the residents are satisfied with the security yet the parking condition still needs to be improved.


# Introduction

Since Toronto is one of the biggest and most wealthy cities in Canada, the existence of huge population makes apartment buildings absolutely necessary to this city. Millions of people are living in Toronto's apartment buildings. This leads to a interesting question: are they really enjoying their stay? On which parts so far are Toronto's apartments doing a great job and which parts are still needed to be improved? Base on the data provided by Opendata Toronto, this project will deeply analyze the real need of Toronto's apartment residents.

The dataset contains building evaluation scores for all evaluated buildings that are registered in the Apartment Building Standards(ABS) program. All areas are reviewed for each building with rates assigned by scores from 1 to 5, with 1 being the worst condition and 5 being the best condition. The overall scores are rated out of 100. However, we transform the overall scores into out of 5 to get a clearer view on the data.



```{r importing data, include=FALSE}
library(tidyverse)
library(opendatatoronto)
library(dplyr)
library(ggplot2)
# get package
package <- show_package("4ef82789-e038-44ef-a478-a8f3590c3eb1")
# get all resources for this package
resources <- list_package_resources("4ef82789-e038-44ef-a478-a8f3590c3eb1")
# identify datastore resources; by default, Toronto Open Data sets datastore resource format to CSV for non-geospatial and GeoJSON for geospatial resources
datastore_resources <- filter(resources, tolower(format) %in% c('csv', 'geojson'))
# load the first datastore resource as a sample
data <- filter(datastore_resources, row_number()==1) %>% get_resource()
attach(data)
```


```{r generalizing data, include=FALSE}
#convert score out of 100 into score out of 5
score_five <- as.numeric(SCORE) / 20
data
```

# Part1: Overview on the data.

```{r histgorams, warning=FALSE}
summary(na.omit(score_five))
par(mfrow = c(2,2))
hist(na.omit(score_five), main="Histogram of Overall Score")
hist(as.numeric(SECURITY), main="Histogram of Security")
hist(as.numeric(ENTRANCE_LOBBY), main="Histogram of Lobby")
hist(as.numeric(PARKING_AREA), main="Histogram of Parking")
```
The average overall score of Toronto apartments is 3.796/5, with the lowest score of 1.85 and the highest score of 5. And half of the apartments are between the score range of 3.5~4.1. From the histogram of overall score, we see the graph is slighly left-skewed, and the score gathers around 3.75. 

Moving onto the other three histogram. The histogram of security is extremely left-skewed, which shows that most of the buildings have a well provided security. The histogram of lobby indicates that most of the residents think their lobby condition is 4 out of 5. However, the histogram of parking condition shows that residents are not very satisfied with the parking condition of the apartments.


# Part2: How are the rating influence the overall score.
```{r linear relation, warning=FALSE}
par(mfrow = c(1,3))
plot(SECURITY, score_five)
plot(ENTRANCE_LOBBY, score_five)
plot(PARKING_AREA, score_five)
```

From the plots above, we find a positive linear relationship between the overall score and each condition score. As the rating on security, lobby and parking goes higher, the overall score of the building increases simultaneously. This implies that all three conditions are important elements that residents care about the buildings.

# Part3: Concluding the quality of Toronto apartments.

```{r boxplot ,warning=FALSE}
element <- c("Overall Score", "Security", "Lobby", "Parking")
boxplot(score_five, as.numeric(SECURITY), as.numeric(ENTRANCE_LOBBY), as.numeric(PARKING_AREA), names = element, horizontal = FALSE, main = "Boxplot of Overall Score and Area Conditions", ylab= "score out of 5")
```

The boxplots above further states the residents' rating on each area condition. The dots on the plots are outliers which are ignored in our study. We should be proud of the security service of Toronto apartments since most of the residents give high scores on it. The condition of lobby is also outstanding with the proofs from the majority. However, the average score of 3 out of 5 of parking condition should be an alert to all the building management. 

# Weakness and Next-step

The dataset was detailed and useful. However, there are more possible elements that are influcing the residents' living condition. For example, the service from building managment, the amount and quality of amenity provided, the nearby community services and so on. There also exist a lack on parking condition rating. For example, some buildings do not have large parking space, but there might be a parking area nearby the building which is also convinent to the residents. 

To improve the survey, we should gather opinions from the residents and analyze what are their real needs beside the ones they are rating in this survey.

# Conclusion:

Residents in Toronto apartments are living in a safe and clean environment with high-level security service and well rated lobby area. Yet they are not very satisfied with the parking condition provided by the building. 


# Reference
@citetidyverse

@rmarkdown

Open Data Dataset. (n.d.). Retrieved September 27, 2020, from https://open.toronto.ca/dataset/apartment-building-evaluation/


